\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-24 document/XSGRB_sample.tex
Update XSGRB_sample.tex

>>>>

	\subsection{GRB151021A (z = 2.330)}
	The data presented here also formed the basis of GCN \#
	18426\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not published
	elsewhere.
	The observation was carried out in RRM starting 44 min af the GRB trigger.
	We detect absorption features from a wide range of ions at z=2.330 
	as well as intervening absorption at $z=1.49$.
